\documentclass{AIAA}
\usepackage{amsfonts,amsmath,amssymb}
\usepackage{graphicx}
\usepackage{color}
\usepackage{url}
\usepackage{hyperref}
\begin{document}
\title{A New Actuator for On-Orbit Inspection}
\author{Benjamin Z. Reinhardt \footnote{Sibley School of Mechanical and Aerospace Engineering, bzr3@cornell.edu, and AIAA Student Member} and Mason A. Peck \footnote{Associate Professor, Sibley School of Mechanical and Aerospace Engineering, Full Member}}
\affiliation{Cornell University, Ithaca, NY, 14850}
%Changelog:
%8/7/2014 - bzr3 - Uploaded for editing 

%note, if it throws a 
\input{tex/abstract.tex} 

\maketitle

\input{tex/nomenclature.tex}
\input{tex/introduction.tex}
\input{tex/background.tex}


%\input{tex/mission_description.tex}

\input{tex/induction_coupler_behaviors.tex}

\input{tex/system.tex}
\input{tex/conclusion.tex}
\section*{Acknowledgments}
This work was supported by NASA NSTRF Grant \#NNX11AN46H %TODO PUT NUMBER HERE
\section*{References}
\bibliographystyle{plain}
\bibliography{biblio.bib}
\end{document}


[1]Why is this repeated whole cloth from the abstract?
[2]I'm not sure that this sentence belongs in this paragraph, but in any case it can't serve as its own paragraph.  Go for at least 3 sentences per paragraph.
[3]Need a transition sentence at the beginning of this paragraph.
[4] This paragraph is not true and needs to be changed iin a way that isn’t comp
[5]This sentence is meant to serve as a conclusion.  The paragraph needs one.  If you don't like this one, write another.
[6]Cite one of the hundreds of papers describing this "non-destructive evaluation" technique.
[7]I moved these two sentences here because they makes more sense in the flow of the paragraph, but now it seems redundant.  Get rid of it?
[8]Deleted because it seems redundant.
[9]replace "small" with a model number and manufacturer
[10]Format correctly
[11]Can you compare this value of mN/W to the force/power for typical ion propulsion, EMFF, and Coulomb approaches offer?  Do so in the conclusion, not here.
[12]Do you have citations for these principles and/or some specific dependencies (linear, etc?)
[13]These two sentences are not connected to the text around them.  Do they belong here?  I have no problem with what’s being said, but why is it being said here?  What larger point is being made?
[14]I have several questions about notation that arise in this section.  Matrices and scalars should be non-bold.  Vectors and tensors should be boldface.  You should not multiply a matrix by a vector or a tensor.  The superscript X notation is used only for matrices (e.g. 3x1 columns of numbers), which would be non-boldface.
[15]This is fine; make all appearances of 6Dof or 6DOF or 6 DoF consistent.
[16]What numbers do you have?
[17]Combine these discrete sentences into a paragraph with an introductory sentence and a conclusion
[18]Here’s where you should compare your experimental results to the scale of forces available from the other technologies, concluding that your concept is not only viable but better in N/W.
